RAS2012: Competition Entry

### 2012-06-17 ras2012-paper/src/main/latex/paper/paper.tex
Benchmarked solutions.
Re-benchmark after the bugfix.
Newly benchmarked results.
Re-evaluate solutions.

@@

In this section, we show the best solutions reached for each data set. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 1 GB of heap space inside Java 7 runtime environment. The specific solver configurations used to reach these solutions may not have been the same every time.

Please note that via the benchmarking functionality of Drools planner (see above), users may be able to fine-tune the algorithm. This fine-tuning can be focused either on providing better solutions or on faster turnaround times.

\include{RDS1.txt-1582}.

\include{RDS2.txt-8948}.

\include{RDS3.txt-11697}.

\include{TOY.txt-808}.

>>>>

\section{Achieved results}

Running the algorithm described above 20 times over each data set, we have compiled a set of results, see Table \ref{table:results}. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 2 GB of heap space inside Java 7 runtime environment.

\begin{table}
\caption{Solution performance per data set.}
\begin{tabular}{c||c|c|c|c|c|c}
\hline \hline
    & Best    & Q1      & Q2      & Q3      & Worst   & Std. dev. \\ 
\hline
TOY & \$808   & \$960   & \$1210  & \$1210  & \$1210  & 164 \\ 
\hline 
1   & \$1435  & \$1695  & \$1930  & \$2856  & \$5612  & 1219 \\ 
\hline 
2   & \$8097  & \$10364 & \$14865 & \$16177 & \$22486 & 4088 \\ 
\hline 
3   & \$10617 & \$13247 & \$15367 & \$17307 & \$21384 & 2986 \\ 
\end{tabular} 
\label{table:results}
\end{table}

Please note that via the benchmarking functionality of Drools Planner (see above), users may be able to fine-tune the algorithm to be focused either on providing better solutions or on faster turnaround times.

For statistics of the resolved systems, see tables \ref{table:TOY-808.tex}, \ref{table:RDS1-1435.tex}, \ref{table:RDS2-8097.tex} and \ref{table:RDS3-10617.tex} respectively.

@@

In this section, we show the best solutions reached for each data set.

\include{TOY-808}
\include{RDS1-1435}
\include{RDS2-8097}
\include{RDS3-10617}
